SCM plan for a troubling company

### 2012-01-11 article.tex
Abstract change

Many companies, especially the small ones, don't see the benefits of SCM in their company and decides to not use it.
This company however have now seen the light and need help to implement it.
This report will go through some aspects in this implementation and will focus on a relatively small software company of 40-50 employees.
We will analyze some of their problems and come up with solutions to them.

@@

\subsection{documentation}
The documentation is modified by whoever changes the API as microsoft doc files on a central fileserver.
Conflicts are avoided by keeping those files open if you're trying to change them.
This has worked quite well but the recent size increase makes problems with people waiting on these files and forgetting to close them a problem.

>>>>

Many companies, especially the small ones, don't see the benefits of SCM in their company and decides to not use it.
This company however have now seen the light and need help to implement it.
This report goes through some aspects in this implementation and focus on a relatively small software company of 40-50 employees.
We analyze some of their problems and come up with solutions in the form of a configuration plan.

@@

\subsection{Documentation}
The documentation is modified by whoever changes the API as microsoft doc files on a central fileserver.
Conflicts are avoided by keeping those files open if you're trying to change them.
This has worked quite well but the recent size increase makes problems with people waiting on these files and forgetting to close them a problem.

\subsection{The build}
